Summer 2025 ToDo

### 2025-04-28 Relations/Paper/Summer_2025_TODO.tex
Minor todo update
Progress on wellfounded, DNE error to fix.

  \item Other ToDo 
  \begin{todolist}
    \item [\done] Make Latex version of WF implications (initial draft).
    \item Verify which implications have and have not been formalized from the image.
    \item (Missing imp) $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$. 
    \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
    \item (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition. 
    \item Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper. I need to go through it and either understand it or come with questions to Friday's meeting.
  \end{todolist}
\end{itemize}
\end{document}

>>>>

  \item Other ToDo 
  \begin{todolist}
    \item [\done] Make Latex version of WF implications (initial draft).
    \item [\done] Verify which implications have and have not been formalized from the image.
    \item (Missing imp) $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$. 
    \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
    \item [\done] (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition. 
    \item [\done] Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper. I need to go through it and either understand it or come with questions to Friday's meeting.
  \end{todolist}
\end{itemize}

\section*{Week starting April 28th}
\begin{itemize}
  \item Below notes from meeting on April 25th.
  \begin{todolist}
    \item Fix Wellfounded.agda after changes made during meeting.
    \item Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
    \item Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper 
    \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution.
    \item (Research item) Go deeper in the related works and see which are most relevant. Make a list of works and give summaries to be used in future papers. 
    \item (Research item) Find a concrete application of generalized Newman's Lemma. 
    \item (Research item) Use TeReSe to create a list of rewrite systems.
    \item (Research item) Work on the missing implicaitons from the paper. So far we believe this is just CR $\to$ CP in the ARS section. 
    \item (Research item) Formalize a first order term rewriting system (I can't remember what the motivation for this was).
    \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counerexamples been shown before?
    \item (Research item) Do we want to reincorporate Knaster Tarski?  
  \end{todolist}
\end{itemize}
\end{document}
